Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-06-14 Multiresolution_framework/ltx/manuscript.tex
edit to the caption of the EM convergence plot

This section is included to provide the interested reader with an overview of the theory for the scaling and wavelet functions that form the basis of the multi-resolution model. Although a deep understanding of the theory presented in this section is not required for an understanding of the key results of the paper, it serves as a reference for implementing the methods.

@@

The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations. The rate of convergence of the EM based algorithm is depicted in Fig.~\ref{fig:MRA-Convergence}. 
\begin{figure}[t]
 	\centering
 		\includegraphics[scale=1]{./Graph/fig8.pdf}
 		\caption{{\bf Convergence of the EM based algorithm}. Representative plot of
the $\mathbf A(\boldsymbol\theta)$ Frobenius norm vs iterations of EM based algorithm. The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.} 
\label{fig:MRA-Convergence}  
 \end{figure}     
% The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets. Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}. Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states. 
The actual connectivity kernel and the decomposition is plotted in Fig.~\ref{fig:KernelEstimate}(A). No assumptions where made about the shape of the kernel. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The large standard deviation is due to the high number of parameters needed to be estimated. The small error in the estimate is attributed to the MRA of the system used to form the estimator. Figs.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively. A total number of 25 basis functions were used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$, respectively. 
\begin{figure}[!t]  
 \centering
\includegraphics{./Graph/fig9.pdf}
\caption{ {\bf Connectivity kernel estimate}. (\textbf{A}) The actual kernel and its components are shown by solid and dashed black lines, respectively. The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.). (\textbf{B},\textbf{C}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
\label{fig:KernelEstimate}
\end{figure}

>>>>

This section is included to provide the interested reader with an overview of the theory for  scaling and wavelet functions that form the basis of the multi-resolution model. Although a deep understanding of the theory presented in this section is not required for an understanding of the key results of the paper, it serves as a reference for implementing the methods.

@@

The EM algorithm was allowed to run until a maximum number of 20 iterations was reached, though typically the change in the transition matrix Frobenius norm dropped below $10^{-6}$ after less than 10 iterations. The rate of convergence of the EM based algorithm is depicted in Fig.~\ref{fig:MRA-Convergence}. 
\begin{figure}[t]
 	\centering
 		\includegraphics[scale=1]{./Graph/fig8.pdf}
 		\caption{{\bf Convergence of the EM based algorithm}. The mean  of
the $\mathbf A(\boldsymbol\theta)$ Frobenius norm over 200 realizations vs iterations of the EM based algorithm. The change in the stopping criterion falls below $10^{-6}$ after less than 10 iterations.} 
\label{fig:MRA-Convergence}  
 \end{figure}     
% The spatial cutoff frequency of the observed field was used to specify the level of decomposition required to represent the field using the wavelets. Using an oversampling parameter of 5, the cutoff spatial frequency was $\nu_{cy} \approx 6.9 $ cycles/mm, obtained by averaging the spectral power of the spatial frequency (over time) from the observations \cite{Scerri2009}. Therefore, wavelets up to level $j=3$ (with the bandwidth $\approx[5,8]$ cycles/mm) can represent the significant spatial characteristics of the field, yielding $n_x = 131$ states. 
The actual connectivity kernel and the decomposition is plotted in Fig.~\ref{fig:KernelEstimate}(A). No assumptions where made about the shape of the kernel. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The large standard deviation is due to the high number of parameters needed to be estimated. The small error in the estimate is attributed to the MRA of the system used to form the estimator. Figs.~\ref{fig:KernelEstimate}(B) and (C) illustrate the kernel scaling and wavelet functions, respectively. A total number of 25 basis functions were used to reconstruct the kernel, comprising 13 and 12 scaling and wavelet functions at $j=1$, respectively. 
\begin{figure}[!t]  
 \centering
\includegraphics{./Graph/fig9.pdf}
\caption{ {\bf Connectivity kernel estimate}. (\textbf{A}) The actual kernel and its components are shown by solid and dashed black lines, respectively. The mean kernel estimates over 200 realizations and confidence interval are shown by the red line and red shaded region ($\pm2$ std.). (\textbf{B},\textbf{C}) Kernel scaling and wavelets functions, respectively, at $j=1$ used in the estimation algorithm.}
\label{fig:KernelEstimate}
\end{figure}
